Trajipaq_sentiment_cr

### 2023-06-19 1. Trajipaq_sentiment/2. Codes/Trajipaq_sentiment_cr.Rmd
merge wgi data set full

trajipaq <- as_factor(trajipaq, only_labelled = TRUE)

@@

WGI_V <- c("vae", "pve", "gee", "rqe", "rle", "cce")

@@

Trajipaq_sentiment_cr <-
  trajipaq %>%
  select("age", # Création de la base de données dédiée à l'analyse.
         "education",
         "sexe",
         "annee_qc",
         "origine",
         "revenu",
         "langue_mat",
         "religion",
         "statut_mat",
         "Q11",
         "VD1",
         "VD2",
         "VD3",
         "VD4",
         "VD5",
         "VI4",
         "vae",
         "vas",
         "van",
         "var",
         "val",
         "vau",
         "pve",
         "pvs",
         "pvn",
         "pvr",
         "pvl",
         "pvu",
         "gee",
         "ges",
         "gen",
         "ger",
         "gel",
         "geu",
         "rqe",
         "rqs",
         "rqn",
         "rqr",
         "rql",
         "rqu",
         "rle",
         "rls",
         "rln",
         "rlr",
         "rll",
         "rlu",
         "cce",
         "ccs",
         "ccn",
         "ccr",
         "ccl",
         "ccu",
         "WGI")

>>>>

```{r}
trajipaq <- as_factor(trajipaq, only_labelled = TRUE)

@@

trajipaq$WGI_2021 <- merge(trajipaq, wgidataset[wgidataset$year == 2021, ],
                           by.x = c("Q11"),
                           by.y = c("countryname"),
                           all.x = TRUE)
```

```{r}
WGI_V <- c("vae", "pve", "gee", "rqe", "rle", "cce")

@@

Trajipaq_sentiment_cr <-
  trajipaq %>%
  select("age", # Création de la base de données dédiée à l'analyse.
         "education",
         "sexe",
         "annee_qc",
         "origine",
         "revenu",
         "langue_mat",
         "religion",
         "statut_mat",
         "Q11",
         "VD1",
         "VD2",
         "VD3",
         "VD4",
         "VD5",
         "VI4",
         "vae",
         "vas",
         "van",
         "var",
         "val",
         "vau",
         "pve",
         "pvs",
         "pvn",
         "pvr",
         "pvl",
         "pvu",
         "gee",
         "ges",
         "gen",
         "ger",
         "gel",
         "geu",
         "rqe",
         "rqs",
         "rqn",
         "rqr",
         "rql",
         "rqu",
         "rle",
         "rls",
         "rln",
         "rlr",
         "rll",
         "rlu",
         "cce",
         "ccs",
         "ccn",
         "ccr",
         "ccl",
         "ccu",
         "WGI",
         "WGI_2021")
